\bf Aggregated Financial Forecasting Calculation in Human-Computer Distributed Computing

### 2020-03-26 Aggregated-Financial-Forecasting-Calculation-in-Human-Computer-Distributed-Computing/paper.tex
Paper sections were fixed.

The idea of a desktop computer screen-saver used for artificial neural networks training was extended in VitoshaTrade\cite{vitosha-trade-01} project where Android Active Wallpaper is used for the same purpose. The project implementation goes on in IICT-BAS and the forecasting capabilities are evolved in the direction of human-computer based distributed computing (crowdsensing\cite{crowdsensing-01}). The users are asked to vote for the future change in the price of Forex currency pairs. Android operating system provides the ideal user interface capabilities for such voting by its widget components. By HTTP protocol the vote of the users is collected on a remote PHP-MySQL based server. As proposed in NSFDE\&A'20, users' votes are classified in four categories: 1) High voting frequency and high guess rate users; 2) Low voting frequency and high guess rate users; 3) High voting frequency and low guess rate users; 4) Low voting frequency and low guess rate users.

This research proposes financial forecasting calculation based on users classification and votes given for particular financial future event. 
%
\section{Conclusions}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

@@

>>>>

The idea of a desktop computer screen-saver used for artificial neural networks training was extended in VitoshaTrade\cite{vitosha-trade-01} project where Android Active Wallpaper is used for the same purpose. The project implementation goes on in IICT-BAS and the forecasting capabilities are evolved in the direction of human-computer based distributed computing (crowdsensing\cite{crowdsensing-01}). The users are asked to vote\cite{voting-01} for the future change in the price of Forex currency pairs. Android operating system provides the ideal user interface capabilities for such voting by its widget components. By HTTP protocol the vote of the users is collected on a remote PHP-MySQL based server. As proposed in NSFDE\&A'20, users' votes are classified in four categories: 1) High voting frequency and high guess rate users; 2) Low voting frequency and high guess rate users; 3) High voting frequency and low guess rate users; 4) Low voting frequency and low guess rate users.

This research proposes financial forecasting calculation based on users classification and votes given for particular financial future event. The rest of this paper is organized as follows: Section 2 describes the problems related to financial forecasting; Section 3 states the ideas for computing in a distributed environment; Section 4 proposes a practical solution for a mobile distributed voting solution; Section 5 reveals some practical experiments and related results; and Section 6 concludes with some suggestions for further work.
%
\section{Financial Time Series}
%
\section{Distributed Computing in Forecasting}
%
\section{Android OS Crowdsensing Solution}
%
\section{Experiments \& Results}
%
\section{Conclusions}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

@@

\bibitem{voting-01} Laukkanen, S., Kangas, A., Kangas, J.: Applying voting theory in natural resource management A case of multiple-criteria group decision support, Journal of Environmental Management, \textbf{64}(2), 127--137 (2002)
